Unsupervised training of maximum-entropy models for lexical selection in rule-based machine translation

### 2015-02-10 2015-eamt-melsa/2015-eamt-melsa.tex
more pruning
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58812 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{description}
\item[Breton--French:] Development of the Breton--French pair has been
  described in \citep{tyers10b}. The bilingual % tyers09b
  dictionaries were not built with polysemy in mind from the outset,
  but some entries were added later to start work on lexical
  selection. The version used in this paper is SVN revision
  41375.\footnote{\url{https://svn.code.sf.net/p/apertium/svn/trunk/apertium-br-fr}}
%  This is the only available machine translation system between Breton
%  and French. It has been developed part-time over a number of years.

@@

For creating the test corpora, and for providing a source language corpus 
for training, and a target language corpus for scoring, we used four parallel corpora: 
\addtolength{\itemsep}{-0.15in}
\begin{itemize}
\item \textbf{Ofis ar Brezhoneg} (\texttt{OAB}): This parallel corpus
  of Breton and French has been collected specifically for
  lexical-selection experiments from translations produced by
  \emph{Ofis ar Brezhoneg} `The Office of the Breton
  language'.%\footnote{In 2010 the administrative status was changed
%    and it was renamed \emph{Ofis Publik ar Brezhoneg} `Public office
%    of the Breton language'. The corpus was published before this date
%    so we use the original name.}  
  It contains some parallel data
  previously described in \cite{tyers09b}, and also some new data. The
  corpus has been made available online through {\sc opus}.\footnote{\url{http://opus.lingfil.uu.se}}
\item \textbf{South-East European Times} (\texttt{SETimes}): Described
  in \cite{tyers10}, this corpus is a multilingual corpus of the
  Balkan languages in the news domain. The Macedonian and English
  portion will be used.
\item \textbf{Open Data Euskadi} (\texttt{OpenData}): This is a Basque
  and Spanish parallel corpus made from the translation memories of
  the \emph{Herri Arduralaritzaren Euskal Erakundea} `Basque Institute
  of Public
  Administration'.\footnote{\url{http://opendata.euskadi.net/w79-contdata/es/contenidos/ds_recursos_linguisticos/memorias_traduccion/es_izo/memorias_traduccion_izo.html}}
\item \textbf{European Parliament Proceedings} (\texttt{EuroParl}):
  Described by \cite{koehn05a}, this is a multilingual corpus of the
  European Union official languages. We are using the English--Spanish
  data from version 7.
\end{itemize}

@@

\begin{table*}
\begin{center}
 \begin{tabular}{|l|r|r|r|r|r|}
    \hline 
    {\bf Pair}      & {\bf Lines} & {\bf SL words} & {\bf TL words} & {\bf Amb. words} & {\bf \% ambig} \\ 
    \hline 
     \texttt{br-fr} & 1,000 & 13,854  & 13,878  & 1,163 & 8.39   \\
    \hline 
     \texttt{mk-en} & 1,000 & 13,441 & 14,228  & 3,872 & 28.80 \\
    \hline 
     \texttt{eu-es} & 1,000 & 7,967 & 11,476  & 1,360  & 17.07 \\
    \hline 
     \texttt{en-es} & 1,000 & 19,882 & 20,944  & 1,469  & 7.38 \\
    \hline 
 \end{tabular} 
\end{center}
 \caption{Statistics about the test corpora. The columns \textbf{amb.\ words} and \textbf{\%~ambig} gives 
    the number of word with more than one translation and the percentage of SL words which have 
    more than one translation respectively.}
  \label{table:test-corp}
\end{table*}

After this process, we selected 1,000 sentence pairs at random for
testing (\texttt{test}), 1,000 for development (\texttt{dev})\footnote{The development corpus  
  was used for checking the value for frequency pruning of features.} and 
left the remainder for training. This is a smaller
number of sentences than used in typical evaluations (such as the WMT
series, \cite{callisonburch2012}), but was motivated by the fact that
the smallest corpus (for Breton--French) after sentence discarding was
only little over 4,000 sentences long. Table~\ref{table:input-corp}
gives statistics about the size of the input corpora, and how many
sentences were left after processing for testing, training and
development. Table~\ref{table:test-corp} gives information about the
test corpora.

@@

\item \textbf{Target language model} (TLM). One method of lexical
  selection is to use the existing machine translation system to
  generate all the possible translations for an input sentence, and
  then score these translations \emph{on-line} on a model of the
  target language. The highest scoring sentence is then picked as
  output. This is the method used by %@@@ \cite{carbonell06} and
  \cite{melero07a}.  
% We used a five-gram language model of surface
%   forms generated from the target-language side of the parallel
%   corpus. %\comment{FSM: Why not a much larger corpus? (I reviewer may ask)}
% %(see section~\ref{sec:eval-corpus}). 
%   This was the best performing system when we compared different
%   approaches, but is impractical for real-world MT because the number
%   of translations to perform grows exponentially with the length of
%   the sentence.  It represents the best that can be achieved using the
%   current systems without access to a parallel corpus. In our work, it
%   was implemented with the IRST language modelling toolkit
%   \cite{federico08a}.
\end{itemize}

>>>>

\begin{description}
\addtolength{\itemsep}{-0.10in}

\item[Breton--French:] Development of the Breton--French pair has been
  described in \citep{tyers10b}. The bilingual % tyers09b
  dictionaries were not built with polysemy in mind from the outset,
  but some entries were added later to start work on lexical
  selection. The version used in this paper is SVN revision
  41375.\footnote{\url{https://svn.code.sf.net/p/apertium/svn/trunk/apertium-br-fr}}
%  This is the only available machine translation system between Breton
%  and French. It has been developed part-time over a number of years.

@@

For creating the test corpora, and for providing a source language corpus 
for training, and a target language corpus for scoring, we used four parallel corpora: 
\begin{itemize}
\addtolength{\itemsep}{-0.10in}
\item \textbf{Ofis ar Brezhoneg} (\texttt{OAB}): This parallel corpus
  of Breton and French has been collected specifically for
  lexical-selection experiments from translations produced by
  \emph{Ofis ar Brezhoneg} `The Office of the Breton
  language'.%\footnote{In 2010 the administrative status was changed
%    and it was renamed \emph{Ofis Publik ar Brezhoneg} `Public office
%    of the Breton language'. The corpus was published before this date
%    so we use the original name.}  
  It contains some parallel data
  previously described in \cite{tyers09b}, and also some new data. The
  corpus has been made available online through {\sc opus}.\footnote{\url{http://opus.lingfil.uu.se}}
\item \textbf{South-East European Times} (\texttt{SETimes}): Described
  in \cite{tyers10}, this corpus is a multilingual corpus of the
  Balkan languages in the news domain. The Macedonian and English
  portion will be used.
\item \textbf{Open Data Euskadi} (\texttt{OpenData}): This is a Basque
  and Spanish parallel corpus made from the translation memories of
  the \emph{Herri Arduralaritzaren Euskal Erakundea} `Basque Institute
  of Public
  Administration'.\footnote{\url{http://opendata.euskadi.net/w79-contdata/es/contenidos/ds_recursos_linguisticos/memorias_traduccion/es_izo/memorias_traduccion_izo.html}}
\item \textbf{European Parliament Proceedings} (\texttt{EuroParl}):
  Described by \cite{koehn05a}, this is a multilingual corpus of the
  European Union official languages. We are using the English--Spanish
  data from version 7.
\end{itemize}

@@

%  \begin{table*}
%  \begin{center}
%   \begin{tabular}{|l|r|r|r|r|r|}
%      \hline 
%      {\bf Pair}      & {\bf Lines} & {\bf SL words} & {\bf TL words} & {\bf Amb. words} & {\bf \% ambig} \\ 
%      \hline 
%       \texttt{br-fr} & 1,000 & 13,854  & 13,878  & 1,163 & 8.39   \\
%      \hline 
%       \texttt{mk-en} & 1,000 & 13,441 & 14,228  & 3,872 & 28.80 \\
%      \hline 
%       \texttt{eu-es} & 1,000 & 7,967 & 11,476  & 1,360  & 17.07 \\
%      \hline 
%       \texttt{en-es} & 1,000 & 19,882 & 20,944  & 1,469  & 7.38 \\
%      \hline 
%   \end{tabular} 
%  \end{center}
%   \caption{Statistics about the test corpora. The columns \textbf{amb.\ words} and \textbf{\%~ambig} gives 
%      the number of word with more than one translation and the percentage of SL words which have 
%      more than one translation respectively.}
%    \label{table:test-corp}
%  \end{table*}

After this process, we selected 1,000 sentence pairs at random for
testing (\texttt{test}), 1,000 for development (\texttt{dev})\footnote{The development corpus  
  was used for checking the value for frequency pruning of features.} and 
left the remainder for training. This is a smaller
number of sentences than used in typical evaluations (such as the WMT
series, \cite{callisonburch2012}), but was motivated by the fact that
the smallest corpus (for Breton--French) after sentence discarding was
only little over 4,000 sentences long. Table~\ref{table:input-corp}
gives statistics about the size of the input corpora, and how many
sentences were left after processing for testing, training and
development. %Table~\ref{table:test-corp} gives information about the
%test corpora.

@@

\item \textbf{Target language model} (TLM). One method of lexical
  selection is to use the existing machine translation system to
  generate all the possible translations for an input sentence, and
  then score these translations \emph{on-line} on a model of the
  target language. The highest scoring sentence is then 
  output. This is the method used by %@@@ \cite{carbonell06} and
  \cite{melero07a}.  
% We used a five-gram language model of surface
%   forms generated from the target-language side of the parallel
%   corpus. %\comment{FSM: Why not a much larger corpus? (I reviewer may ask)}
% %(see section~\ref{sec:eval-corpus}). 
%   This was the best performing system when we compared different
%   approaches, but is impractical for real-world MT because the number
%   of translations to perform grows exponentially with the length of
%   the sentence.  It represents the best that can be achieved using the
%   current systems without access to a parallel corpus. In our work, it
%   was implemented with the IRST language modelling toolkit
%   \cite{federico08a}.
\end{itemize}
